\chapter{Robustness Check\label{ch:robustness}}

\section{External Validity}

Our models were able to capture a significant proportion of the variability in self-employment entry, with Pseudo $R^2$ coefficients surpassing 0.5. There are however, areas that could benefit from further exploration, a more comprehensive set of variables being expected to add to the current research in insightful ways. In terms of education and its effect on self-employment rates, it is known that in most OECD countries men and women reach similar attainment levels (Charles and Bradley, 2002). However, there is a persistent gender gap in \textit{educational choices} across genders, with women being a majority in fields like health and education, and underrepresented in more technical programs, like hard sciences and engineering (Charles and Bradley, 2002). Given that our data doesn’t capture field of study, but only level of educational attainment and industry of choice, one can suspect that similar education level might not bring the same effects across individuals, especially since technical fields are more often associated with both entrepreneurship of innovation, as well as persistent gender gaps. 

Entrepreneurship is often associated with \textit{“greater flexibility in terms of an individual’s discretion over the length, location and scheduling of their work time”} (Quinn, 1980). It is thus expected for people with poor health or disabilities to have a higher probability of self-employment, as a way to avoid workplace discrimination (Quinn, 1980). The relation between self-employment and ill-health or disability could be an important control for self-employment decisions, one to be explored with more generous data.  Research also finds that children act as a greater impediment on a female’s entrepreneurial career than that of a male, a factor our model does not control for due to data limitations. In the future, the role of children on parents’ decisions to become entrepreneurs, as well as quit self-employment could be studied to capture whether changes of societal perceptions on parenthood have occurred, or whether traditional parenting patterns are still in place.  

Our review of sociological sources discusses the influence of social capital on entrepreneurship ventures. To that end, The Entrepreneurial Group challenged ingrained conceptions in research and public discourse that only model individual decisions. The lack of data combining both firm characteristics and individual controls does not allow to control for this factor, leaving open questions about the role of co-ownership in business formation and success patterns. 